
---
title: "Course Project: Shiny Application and Reproducible Pitch"
author: "Malihehe Shomali"
date: "February 28, 2018"
output: ioslides_presentation
---


## Overview 
- Final project for "Developing Data Product" as part of the Data Science Specialization
- Shiny is used to build the presentation
- The Presentation was built  in RStudio to pitch the data product for the application
- The application is developed using data available from Motor Trend Car Road Tests

## The summary of dataset "mtcars" 
```{r mtcars, echo = TRUE,  comment=""}
head(mtcars, 1)
summary(mtcars)
```


```{r , echo = FALSE}
library(plotly)
library(ggplot2)
```

## Application
- The application is developed to help you to find the best car for your purpose
- It allows you to select a desirable car based on miles per gallon vs. the horse power in three category of cylinder sizes, 4, 6, and 8.
- The application can be find at:
http://rpubs.com/shomali/331206 

```{r, echo=FALSE}
mtcars$gear <- factor(mtcars$gear,levels=c(3,4,5),
  	labels=c("3gears","4gears","5gears")) 
mtcars$am <- factor(mtcars$am,levels=c(0,1),
  	labels=c("Automatic","Manual")) 
mtcars$cyl <- factor(mtcars$cyl,levels=c(4,6,8),
   labels=c("4cyl","6cyl","8cyl")) 
```

## Miles per Gallon vs. Horsepower 
- Combination of gears and cylinders in each facet

```{r, echo=FALSE}
qplot(hp, mpg, data=mtcars,color=am,
   facets=gear~cyl, size=I(3),
   xlab="Horsepower", ylab="Miles per Gallon") 
```
